### 2019-12-09 chX_backmatter.tex
fixes to backmatter

\begin{itemize}
  \item \textbf{Differential Network Medicine}, Antwerp, Belgium, 4-6 December 2013.
  \item \textbf{BeNeLux Bioinformatics Conference}, Brussels, Belgium, 9-10 December 2013.
  \item \textbf{OncoPoint}, Ghent, Belgium, 6 February 2014.
  \item \textbf{AISTATS}, Reykjavik, Iceland, 22-25 April 2014.
  \item \textbf{N2N Annual Symposium}, Ghent, Belgium, 21 May 2014.
  \item \textbf{Bioinformatics N2N Conference}, Ghent, Belgium, 21 May 2014.
  \item \textbf{BENELEARN}, Brussels, Belgium, 6 June 2014.
  \item \textbf{BeNeLux Bioinformatics Conference}, Luxembourg, 8-9 December 2014.
  \item \textbf{OncoPoint}, Ghent, Belgium, 11 February 2015.
  \item \textbf{Big Data to Bedside}, Ghent, Belgium, 1-2 April 2015.
  \item \textbf{BIG N2N symposium}, Ghent, Belgium, 21 May 2015.
  \item \textbf{BeNeLux Bioinformatics Conference}, Antwerp, Belgium, 7-8 December 2015
  \item \textbf{Single Cell Biology Workshop}, Ghent, Belgium, 15 January 2016.
  \item \textbf{Single Cell Biology}, Hinxton, United Kingdom, 8-10 March 2016.
  \item \textbf{BIG N2N symposium}, Ghent, Belgium, 19 May 2016.
  \item \textbf{CYTO}, Seattle, United States of America, 11-15 June 2016.
  \item \textbf{BENELEARN}, Kortrijk, Belgium, 12-13 September 2016.
  \item \textbf{Single Cell Genomics}, Hinxton, United Kingdom, 14-16 September 2016.
  \item \textbf{Single Cell Biology Workshop}, Ghent, Belgium, 15 January 2016.
  \item \textbf{VIB Seminar}, Veldhoven, Netherlands, 27-28 April 2017.
  \item \textbf{Keystone Symposia: Single Cell Omics}, Stockholm, Zweden, 26-30 May 2017. 
  \item \textbf{BeNeLux Bioinformatics Conference}, Louvain, België, 13-14 December 2017.
  \item \textbf{Single Cell Biology}, Hinxton, United Kingdom, 8-10 March 2018.
  \item \textbf{Keystone Symposia: Single Cell Biology}, Colorado, USA, 13-17 January 2019.
  \item \textbf{Human Cell Atlas}, Toronto, Canada, 29-31 July 2019.
\end{itemize}

@@

\begin{itemize}
  \item Cannoodt R., Ruyssinck J., De Preter K., Dhaene T., Saeys Y. : Network inference by integrating biclustering and feature selection. \textbf{BeNeLux Bioinformatics Conference}, Brussels, Belgium, 9-10 December 2013.
  \item Cannoodt R., Ruyssinck J., De Preter K., Dhaene T., Saeys Y. : Network inference by integrating biclustering and feature selection. \textbf{IRC bioinformatics day}, Ghent, Belgium, 23 November 2013.
  \item Cannoodt R., De Preter K., Saeys Y. : Differential network inference for pediatric cancers. \textbf{Maestra meeting}, Ghent, Belgium, 14 March 2014.
  \item Cannoodt R., Beckers A., Van Cauwenbergh C., Speleman F., Saeys Y., De Preter K. : Differential module analysis in neuroblastoma regulatory networks. \textbf{Oncopoint}, Ghent, Belgium, 11 February 2015.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y.: Inferring developmental chronologies from single cell RNA, \textbf{BeNeLux Bioinformatics Conference}, Antwerp, Belgium, 7-8 December 2015.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y.: Inferring trajectories along dynamic processes from single-cell RNA-seq data. \textbf{Jean-Luc Doumont workshop}, Ghent, Belgium, 17 December 2015.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : SCORPIUS: Inferring trajectories along dynamic processes form single-cell RNA-seq data. \textbf{Single Cell Biology Workshop}, Ghent, Belgium, 15 January 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Improving marker gene discovery from high-dimensional single-cell snapshot data. \textbf{CYTO}, Seattle, United States of America, 11-15 June 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. \textbf{BENELEARN}, Kortrijk, Belgium, 12-13 September 2016.
  \item Cannoodt R., Saelens W., Sichien D., Tavernier S., Janssens S., Guilliams M., Lambrecht B., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with SCORPIUS identifies novel modules in dendritic cell development. \textbf{VIB Seminar}, Veldhoven, Nederland, 27-28 april 2017.
  \item Cannoodt R., Saelens W. : Automated building and unit testing, Docker and Singularity. \textbf{VIB Developers Meeting}, Ghent, Belgium, 25 January 2019.
  \item Cannoodt R., Saelens W., Todorov H., Saeys Y. : dynbenchmark, Assessing Accuracy, Robustness and Usability of Single-Cell Trajectory Inference methods. \textbf{Keystone Symposia: Single Cell Biology}, Colorado, USA, 13-17 January 2019.
\end{itemize}

@@

\begin{itemize}
  \item Cannoodt R., Ruyssinck J., De Preter K., Dhaene T., Saeys Y.: Network Inference by Integrating Biclustering and Feature Selection. \textbf{N2N Annual Symposium}, Ghent, Belgium, 21 May 2014.
  \item Cannoodt R., Van Cauwenbergh C., Beckers A., Speleman F., De Preter K., Saeys Y.: Differential Module Analysis in Neuroblastoma Regulatory Networks. \textbf{BeNeLux Bioinformatics Conference} 2014, Luxembourg, Belgium, 8-9 December 2014.
  \item Cannoodt R., Beckers A., Van Cauwenbergh C., Speleman F., De Preter K., Saeys Y.: Differential Module Analysis in Neuroblastoma Regulatory Networks, \textbf{BIG N2N symposium}, Ghent, Belgium, 21 May 2015.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. Single Cell Biology, Hinxton, United Kingdom, 8-10 March 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. \textbf{BIG N2N symposium}, \textbf{BIG N2N symposium}, Ghent, Belgium, 19 May 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Improving marker gene discovery from high-dimensional single-cell snapshot data. CYTO, Seattle, United States of America, 11-15 June 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. BENELEARN 2016, Kortrijk, Belgium, 12-13 September 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. Single Cell Genomics, Hinxton, United Kingdom, 14-16 September 2016.
  \item Cannoodt R., Saelens W., Sichien D., Tavernier S., Janssens S., Guilliams M., Lambrecht B., De Preter K., Saeys Y.: Unbiased modelling of dynamic processes with SCORPIUS identifies novel modules in dendritic cell development. \textbf{VIB Seminar}, Veldhoven, Netherlands, 27-28 April 2017.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y.: True single cell network inference: Modelling gene regulation of individual cells. \textbf{Keystone Symposia: Single Cell Omics}, Stockholm, Zweden, 26-30 May 2017. 
  \item Cannoodt R., Saelens W., Todorov H., Saeys Y.: Generalised framework for and comparison of 24 trajectory inference methods. \textbf{BeNeLux Bioinformatics Conference}, Louvain, België, 13-14 December 2017.
  \item Cannoodt R., Saelens W., Todorov H., Saeys Y. : A comparison of single-cell trajectory inference methods: towards more accurate and robust tools. \textbf{Single Cell Biology}, Hinxton, United Kingdom, 8-10 March 2018.
  \item Cannoodt R., Saelens W. : dynbenchmark, Assessing Accuracy, Robustness and Usability of Single-Cell Trajectory Inference methods. \textbf{Keystone Symposia: Single Cell Biology}, Colorado, USA, 13-17 January 2019.
\end{itemize}

@@

% thanking:
% the people who brought me soup and sandwiches (look up names)
% the people who tried to use the PRISM cluster but couldn't

>>>>

\begin{itemize}
  \item \textbf{Differential Network Medicine}, Antwerp, Belgium, 4-6 December 2013.
  \item \textbf{BeNeLux Bioinformatics Conference}, Brussels, Belgium, 9-10 December 2013.
  \item \textbf{OncoPoint}, Ghent, Belgium, 6 February 2014.
  \item \textbf{AISTATS}, Reykjavik, Iceland, 22-25 April 2014.
  \item \textbf{N2N Annual Symposium}, Ghent, Belgium, 21 May 2014.
  \item \textbf{Bioinformatics N2N Conference}, Ghent, Belgium, 21 May 2014.
  \item \textbf{BENELEARN}, Brussels, Belgium, 6 June 2014.
  \item \textbf{BeNeLux Bioinformatics Conference}, Luxembourg, 8-9 December 2014.
  \item \textbf{OncoPoint}, Ghent, Belgium, 11 February 2015.
  \item \textbf{Big Data to Bedside}, Ghent, Belgium, 1-2 April 2015.
  \item \textbf{BIG N2N symposium}, Ghent, Belgium, 21 May 2015.
  \item \textbf{BeNeLux Bioinformatics Conference}, Antwerp, Belgium, 7-8 December 2015
  \item \textbf{Single Cell Biology Workshop}, Ghent, Belgium, 15 January 2016.
  \item \textbf{Single Cell Biology}, Hinxton, United Kingdom, 8-10 March 2016.
  \item \textbf{BIG N2N symposium}, Ghent, Belgium, 19 May 2016.
  \item \textbf{CYTO}, Seattle, USA, 11-15 June 2016.
  \item \textbf{BENELEARN}, Kortrijk, Belgium, 12-13 September 2016.
  \item \textbf{Single Cell Genomics}, Hinxton, United Kingdom, 14-16 September 2016.
  \item \textbf{Single Cell Biology Workshop}, Ghent, Belgium, 15 January 2016.
  \item \textbf{VIB Seminar}, Veldhoven, Netherlands, 27-28 April 2017.
  \item \textbf{Keystone Symposia: Single Cell Omics}, Stockholm, Sweden, 26-30 May 2017. 
  \item \textbf{BeNeLux Bioinformatics Conference}, Louvain, Belgium, 13-14 December 2017.
  \item \textbf{Single Cell Biology}, Hinxton, United Kingdom, 8-10 March 2018.
  \item \textbf{Keystone Symposia: Single Cell Biology}, Colorado, USA, 13-17 January 2019.
  \item \textbf{Human Cell Atlas}, Toronto, Canada, 29-31 July 2019.
\end{itemize}

@@

\begin{itemize}
  \item Cannoodt R., Ruyssinck J., De Preter K., Dhaene T., Saeys Y. : Network inference by integrating biclustering and feature selection. \textbf{BeNeLux Bioinformatics Conference}, Brussels, Belgium, 9-10 December 2013.
  \item Cannoodt R., Ruyssinck J., De Preter K., Dhaene T., Saeys Y. : Network inference by integrating biclustering and feature selection. \textbf{IRC bioinformatics day}, Ghent, Belgium, 23 November 2013.
  \item Cannoodt R., De Preter K., Saeys Y. : Differential network inference for pediatric cancers. \textbf{Maestra meeting}, Ghent, Belgium, 14 March 2014.
  \item Cannoodt R., Beckers A., Van Cauwenbergh C., Speleman F., Saeys Y., De Preter K. : Differential module analysis in neuroblastoma regulatory networks. \textbf{Oncopoint}, Ghent, Belgium, 11 February 2015.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y.: Inferring developmental chronologies from single cell RNA, \textbf{BeNeLux Bioinformatics Conference}, Antwerp, Belgium, 7-8 December 2015.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y.: Inferring trajectories along dynamic processes from single-cell RNA-seq data. \textbf{Jean-Luc Doumont workshop}, Ghent, Belgium, 17 December 2015.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : SCORPIUS: Inferring trajectories along dynamic processes from single-cell RNA-seq data. \textbf{Single Cell Biology Workshop}, Ghent, Belgium, 15 January 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Improving marker gene discovery from high-dimensional single-cell snapshot data. \textbf{CYTO}, Seattle, USA, 11-15 June 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. \textbf{BENELEARN}, Kortrijk, Belgium, 12-13 September 2016.
  \item Cannoodt R., Saelens W., Sichien D., Tavernier S., Janssens S., Guilliams M., Lambrecht B., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with SCORPIUS identifies novel modules in dendritic cell development. \textbf{VIB Seminar}, Veldhoven, Netherlands, 27-28 april 2017.
  \item Cannoodt R., Saelens W. : Automated building and unit testing, Docker and Singularity. \textbf{VIB Developers Meeting}, Ghent, Belgium, 25 January 2019.
  \item Cannoodt R., Saelens W., Todorov H., Saeys Y. : dynbenchmark, Assessing Accuracy, Robustness and Usability of Single-Cell Trajectory Inference methods. \textbf{Keystone Symposia: Single Cell Biology}, Colorado, USA, 13-17 January 2019.
\end{itemize}

@@

\begin{itemize}
  \item Cannoodt R., Ruyssinck J., De Preter K., Dhaene T., Saeys Y.: Network Inference by Integrating Biclustering and Feature Selection. \textbf{N2N Annual Symposium}, Ghent, Belgium, 21 May 2014.
  \item Cannoodt R., Van Cauwenbergh C., Beckers A., Speleman F., De Preter K., Saeys Y.: Differential Module Analysis in Neuroblastoma Regulatory Networks. \textbf{BeNeLux Bioinformatics Conference} 2014, Luxembourg, Belgium, 8-9 December 2014.
  \item Cannoodt R., Beckers A., Van Cauwenbergh C., Speleman F., De Preter K., Saeys Y.: Differential Module Analysis in Neuroblastoma Regulatory Networks, \textbf{BIG N2N symposium}, Ghent, Belgium, 21 May 2015.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. Single Cell Biology, Hinxton, United Kingdom, 8-10 March 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. \textbf{BIG N2N symposium}, Ghent, Belgium, 19 May 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Improving marker gene discovery from high-dimensional single-cell snapshot data. CYTO, Seattle, USA, 11-15 June 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. BENELEARN 2016, Kortrijk, Belgium, 12-13 September 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. Single Cell Genomics, Hinxton, United Kingdom, 14-16 September 2016.
  \item Cannoodt R., Saelens W., Sichien D., Tavernier S., Janssens S., Guilliams M., Lambrecht B., De Preter K., Saeys Y.: Unbiased modelling of dynamic processes with SCORPIUS identifies novel modules in dendritic cell development. \textbf{VIB Seminar}, Veldhoven, Netherlands, 27-28 April 2017.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y.: True single cell network inference: Modelling gene regulation of individual cells. \textbf{Keystone Symposia: Single Cell Omics}, Stockholm, Sweden, 26-30 May 2017. 
  \item Cannoodt R., Saelens W., Todorov H., Saeys Y.: Generalised framework for and comparison of 24 trajectory inference methods. \textbf{BeNeLux Bioinformatics Conference}, Louvain, Belgium, 13-14 December 2017.
  \item Cannoodt R., Saelens W., Todorov H., Saeys Y. : A comparison of single-cell trajectory inference methods: towards more accurate and robust tools. \textbf{Single Cell Biology}, Hinxton, United Kingdom, 8-10 March 2018.
  \item Cannoodt R., Saelens W. : dynbenchmark, Assessing Accuracy, Robustness and Usability of Single-Cell Trajectory Inference methods. \textbf{Keystone Symposia: Single Cell Biology}, Colorado, USA, 13-17 January 2019.
\end{itemize}

@@

I was told that the end of the dissertation is the right place to thank friends, family, and colleagues for their continued support during my PhD. Nobody ever specified \textit{which} end of the book. This is not the right end you're looking at.

Hello there! Did you stumble across this phrase by accident, 
or are you looking for what I think you're looking for?
